Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-08-13 paper/paper.tex
Start thinking about experiments
Remember to revert this commit later

\author{Ruth Hoffmann \and Ciaran McCreesh\thanks{This work was supported by the Engineering and Physical Sciences
    Research Council [grant number EP/K503058/1]} \\
University of Glasgow, Glasgow, Scotland \\
ruth.hoffmann@glasgow.ac.uk \and c.mccreesh.1@research.gla.ac.uk}

\pdfinfo{
    /Title (Between Subgraph Isomorphism and Maximum Common Subgraph)
    /Author (Ruth Hoffmann and Ciaran McCreesh)
}

@@

>>>>

\author{Ruth Hoffmann \and Ciaran McCreesh\thanks{This work was supported by the Engineering and Physical Sciences
Research Council [grant number EP/K503058/1]} \and Craig Reilly \\
University of Glasgow, Glasgow, Scotland \\
ruth.hoffmann@glasgow.ac.uk \and \{c.mccreesh.1,c.reilly.2\}@research.gla.ac.uk}

\pdfinfo{
    /Title (Between Subgraph Isomorphism and Maximum Common Subgraph)
    /Author (Ruth Hoffmann and Ciaran McCreesh and Craig Reilly)
}

@@

\subsection{Induced}

Comparison with the clique and CP models.

\subsection{Non-Induced}

Just results.

\subsection{Parallel Search}

\subsection{Filtering and Propagation}

\subsubsection{Initial Domain Sizes}

Remember loops can make this overly optimistic if we just take the products!

\subsubsection{Is Path Filtering Useful?}
